Covariate analysis of ROSMAP reprocessed counts (with TMM normalisation)

### 2017-03-07 code/Rmd/ROSMAP_RNASeq_Reprocessed_TMM.Rmd
Minor modifications

# Get picard metrics from synapse
METADATA.PICARD_ID <- 'syn8380366'
ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA.PICARD_ID
METADATA.PICARD_FPATHS <- untar(synGet(METADATA.PICARD_ID)@filePath, list = TRUE)
METADATA.PICARD_FPATHS = METADATA.PICARD_FPATHS[grep('picard.CombinedMetrics.csv', METADATA.PICARD_FPATHS)]
METADATA.PICARD <- plyr::ldply(METADATA.PICARD_FPATHS, read.csv)

>>>>

# Get picard metrics from synapse
METADATA.PICARD_ID <- 'syn8380366'
ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA.PICARD_ID
METADATA.PICARD_FPATHS <- untar(synGet(METADATA.PICARD_ID)@filePath, list = FALSE, exdir = getwd())
METADATA.PICARD_FPATHS <- untar(synGet(METADATA.PICARD_ID)@filePath, list = TRUE, exdir = getwd())
METADATA.PICARD_FPATHS = METADATA.PICARD_FPATHS[grep('picard.CombinedMetrics.csv', METADATA.PICARD_FPATHS)]
METADATA.PICARD <- plyr::ldply(METADATA.PICARD_FPATHS, read.csv)
